The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

###Research Question  
Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?

>>>>

###Research Question  
Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
